Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-23 data_appendix.Rmd
Fixed typo

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, dept0, urb_rur) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```

>>>>

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur) %>% 
  mutate(year = 2005,
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```
